Paper notes

### 2019-07-24 paper_notes.Rmd
uti 0, to simplify
Add files via upload

f <- function(p,M,x,n){
  if (x  <= (n*p)){U <- (x/(n*p))}
  else {U <- M + ((1-(x/n))*(1-M))/(1-p)}
 # else {U <- (2-M) + (((M-1)*x)/(n*p))} M + ((1-(x/n))*(1-M))/(1-p)}
  round(U,digits = 3)
 # print(U)
}

@@

```
\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- <- this is a command to appear in pdf -->
<!-- command not to appear in pdf -->

@@

```{r moore, echo=FALSE, fig.cap="utility in Moore 8 patches; desired fraction 50%, M=0.6, Z=1"}

f0m <- f(0.5,0.6,0,8)
f1m <- f(0.5,0.6,1,8)
f2m <- f(0.5,0.6,2,8)
f3m <- f(0.5,0.6,3,8)
f4m <- f(0.5,0.6,4,8)
f5m <- f(0.5,0.6,5,8)
f6m <- f(0.5,0.6,6,8)
f7m <- f(0.5,0.6,7,8)
f8m <- f(0.5,0.6,8,8)

utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
concentrationm <- c(0:8)

# print(utilitym)
plot(concentrationm,utility_Moore)
```

@@

f0t6 <- f(0.5,0.6,0,6)
f1t6 <- f(0.5,0.6,1,6)
f2t6<- f(0.5,0.6,2,6)
f3t6 <- f(0.5,0.6,3,6)
f4t6 <- f(0.5,0.6,4,6)
f5t6 <- f(0.5,0.6,5,6)
f6t6 <- f(0.5,0.6,6,6)

utilityt6 <- c(f0t6,f1t6,f2t6,f3t6,f4t6,f5t6,f6t6)
concentrationt6 <- c(0:6)

# print(utilityt8)
plot(concentrationt6,utilityt6)

@@

f0m <- f(0.5,1,0,8)
f1m <- f(0.5,1,1,8)
f2m <- f(0.5,1,2,8)
f3m <- f(0.5,1,3,8)
f4m <- f(0.5,1,4,8)
f5m <- f(0.5,1,5,8)
f6m <- f(0.5,1,6,8)
f7m <- f(0.5,1,7,8)
f8m <- f(0.5,1,8,8)

utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
concentrationm <- c(0:8)

# print(utilitym)
plot(concentrationm,utility_Moore)
```

@@

f0m <- f(0.5,0,0,8)
f1m <- f(0.5,0,1,8)
f2m <- f(0.5,0,2,8)
f3m <- f(0.5,0,3,8)
f4m <- f(0.5,0,4,8)
f5m <- f(0.5,0,5,8)
f6m <- f(0.5,0,6,8)
f7m <- f(0.5,0,7,8)
f8m <- f(0.5,0,8,8)

utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
concentrationm <- c(0:8)

# print(utilitym)
plot(concentrationm,utility_Moore)
```

@@

```{r integr, fig.pos='h' , out.widh = '100%', fig.aign='center', fig.cap="Even subgroups ethnicityXvalueXses (12,5% of population each), utility = 0, beta = 100, M = 0.6", echo=FALSE, include=TRUE}

knitr::include_graphics("C:/Users/rocpa/OneDrive/Desktop/upload/integration_0.jpg")

>>>>

library(Hmisc)

#old
# f <- function(p,M,x,n){
#  if (x  <= (n*p)){U <- (x/(n*p))}
#  else {U <- M + ((1-(x/n))*(1-M))/(1-p)}
 # else {U <- (2-M) + (((M-1)*x)/(n*p))} M + ((1-(x/n))*(1-M))/(1-p)}
#  round(U,digits = 3)
# }

#f_dist <- function(o,ot,M,i,S){
#  if (abs(o-ot) < i) {
#    U <- (abs(o-ot)/i) * S
#    }else if (abs(o-ot) > i){
#      U <- M + ((1-abs(o-ot))*(1-M))/(1-i)
#    }else{
#        U <- 1}
#  round(U,digits = 3)
#  }

#f_val <- function(o,ot,M,i,S){
# if (round(abs(o-ot), digits=2) >= i) {
#    U <- 1
#  }else {
#      U <- # (1 - (1-(abs(o-ot))/i) * S)
#         1 -  (M + ((1-(1-abs(o-ot)))/(1-M))/(1-(1-i)))
#       1 - (M + ((1-(1-abs(o-ot)))*(1-M))/(1-(1-i)))
#    }
#  round(U,digits = 3)
#  }

#f_val_repr <- function(sim,M,i,S){
#  if (sim <= i) {
#    U <- sim/i * S
#     }else if (sim > i){
# U <- M + ((1-sim)*(1-M))/(1-i)
#    }else{
#         U <- 1}
#   round(U,digits = 3)
#   }

@@

```{r value_similarity, echo=FALSE, }

f_val <- function(o,ot,M,i,S){
  if (round(abs(o-ot), digits=2) <= i) {
    U <- 1
    }else{
      U <- (M + ((1-(round(abs(o-ot), digits=2)))*(1-M))/(1-i)) * S
    }
  round(U,digits = 2)
  }

i <- 0.2
S  <- 1
M <- 0

#  f_dist <- (o,ot,M,i,S)

for (o in seq (0.0,1.0, by = 0.1)){

fv0d2 <- f_val(o,0,M,i,S)
fv1d2 <- f_val(o,0.1,M,i,S)
fv2d2 <- f_val(o,0.2,M,i,S)
fv3d2 <- f_val(o,0.3,M,i,S)
fv4d2 <- f_val(o,0.4,M,i,S)
fv5d2 <- f_val(o,0.5,M,i,S)
fv6d2 <- f_val(o,0.6,M,i,S)
fv7d2 <- f_val(o,0.7,M,i,S)
fv8d2 <- f_val(o,0.8,M,i,S)
fv9d2 <- f_val(o,0.9,M,i,S)
fv10d2 <- f_val(o,1.0,M,i,S)

value_mean_neighborhood <- seq(0.0, 1.0, by = 0.1)
Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
name <- paste0("Ethnic weight i = ", o,";distance desired i = ",i,"; M = ",M,"; S = ",S)

plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility",  main = "Value Utility for neighborhood j of agent i",  sub = name)

report <- paste0("M = ",M," ??? S = ",S," ??? Ethnic weight i = ",o, " ??? desired distance i = ",i," ??? Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), " ??? Utility ij = ", Utility_V)

print(report)

}

\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- <- this is a command to appear in pdf -->
<!-- command not to appear in pdf -->

```{ethnic utility, moore neighborhood}

f_eth <- function(p,M,x,n,S){
  if (x  < (n*p)){
    U <- (x / (n*p)) * S
    }else if (x > (n*p)){
      U <- M + ((1-(x/n))*(1-M))/(1-p)
    }else{
        U <- 1}
  round(U,digits = 2)
}

# f2 <- function(p,M,x,n,S)

p = 0.5
M = 1
S = 1

f0m <- f_eth(p,M,0,8,S)
f1m <- f_eth(p,M,1,8,S)
f2m <- f_eth(p,M,2,8,S)
f3m <- f_eth(p,M,3,8,S)
f4m <- f_eth(p,M,4,8,S)
f5m <- f_eth(p,M,5,8,S)
f6m <- f_eth(p,M,6,8,S)
f7m <- f_eth(p,M,7,8,S)
f8m <- f_eth(p,M,8,8,S)

ethnic_concentration_neighborhood <- seq(0.0, 0.8, length.out = 9)
Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)

# print(utilitym)
print(c("Ethnic Utility",Utility_E)) 
plot(ethnic_concentration_neighborhood,Utility_E,title("Ethnic Utility"))

```{r testing logistic}

prob <- function(l,s,t,d,p,q){1 / (1 + exp(-l*(s-t)) + exp(-d*(p-q)))}

prob1 <- prob(100,300,100,1,100,100)
plot(prob1)
```

@@

@@

# f0t6 <- f(0.5,0.6,0,6)
# f1t6 <- f(0.5,0.6,1,6)
# f2t6<- f(0.5,0.6,2,6)
# f3t6 <- f(0.5,0.6,3,6)
# f4t6 <- f(0.5,0.6,4,6)
# f5t6 <- f(0.5,0.6,5,6)
# f6t6 <- f(0.5,0.6,6,6)

# utilityt6 <- c(f0t6,f1t6,f2t6,f3t6,f4t6,f5t6,f6t6)
# concentrationt6 <- c(0:6)

# print(utilityt8)
# plot(concentrationt6,utilityt6)

@@

# f0m <- f(0.5,1,0,8)
# f1m <- f(0.5,1,1,8)
# f2m <- f(0.5,1,2,8)
# f3m <- f(0.5,1,3,8)
# f4m <- f(0.5,1,4,8)
# f5m <- f(0.5,1,5,8)
# f6m <- f(0.5,1,6,8)
# f7m <- f(0.5,1,7,8)
# f8m <- f(0.5,1,8,8)

# utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
# concentrationm <- c(0:8)

# print(utilitym)
# plot(concentrationm,utility_Moore)
```

@@

# f0m <- f(0.5,0,0,8)
# f1m <- f(0.5,0,1,8)
# f2m <- f(0.5,0,2,8)
# f3m <- f(0.5,0,3,8)
# f4m <- f(0.5,0,4,8)
# f5m <- f(0.5,0,5,8)
# f6m <- f(0.5,0,6,8)
# f7m <- f(0.5,0,7,8)
# f8m <- f(0.5,0,8,8)

# utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
# concentrationm <- c(0:8)

# print(utilitym)
# plot(concentrationm,utility_Moore)
```

@@
